Higher-Order unification for free!

### 2024-05-13 paper/appendix.tex
fm -> to, fapp -> o-app, flam -> o-app

  type decompl-subst map -> map -> ho.subst -> 
    fo.fsubst -> fo.fsubst -> o.
  decompl-subst _ [A|_] _ _ _ :- fail.
  decompl-subst _ [] _ F F.
  decompl-subst Map [mapping (fv VO) (hv VM _)|Tl] H F F2 :- 
    mem.set? VM H T, !, 
    ho.deref-assmt H T TTT,
    abs->lam TTT T', tm->fm Map T' T1, 
    fo.eta-contract T1 T2, mem.assign VO F T2 F1,
    decompl-subst Map Tl H F1 F2. 
  decompl-subst Map [mapping _ (hv VM _)|Tl] H F F2 :- 
    mem.unset? VM H, decompl-subst Map Tl H F F2.

  type tm->fm map -> ho.tm -> fo.fm -> o.
  tm->fm _ (ho.con C)  (fo.fcon C).
  tm->fm L (ho.lam B1) (fo.flam B2) :- 
    pi x y\ tm->fm _ x y => tm->fm L (B1 x) (B2 y).
  tm->fm L (ho.app L1) T :- map (tm->fm L) L1 [Hd|Tl], 
    fo.mk-app Hd Tl T.
  tm->fm L (ho.uva VM TL) T :- mem L (mapping (fv VO) (hv VM _)), 
    map (tm->fm L) TL T1, fo.mk-app (fo.fuva VO) T1 T.

>>>>

  type decompl-subst map -> map -> ho.subst -> 
    fo.fsubst -> fo.fsubst -> o.
  decompl-subst _ [A|_] _ _ _ :- fail.
  decompl-subst _ [] _ F F.
  decompl-subst Map [mapping (fv VO) (hv VM _)|Tl] H F F2 :- 
    mem.set? VM H T, !, 
    ho.deref-assmt H T TTT,
    abs->lam TTT T', tm->to Map T' T1, 
    fo.eta-contract T1 T2, mem.assign VO F T2 F1,
    decompl-subst Map Tl H F1 F2. 
  decompl-subst Map [mapping _ (hv VM _)|Tl] H F F2 :- 
    mem.unset? VM H, decompl-subst Map Tl H F F2.

  type tm->to map -> ho.tm -> fo.to -> o.
  tm->to _ (ho.con C)  (fo.o-con C).
  tm->to L (ho.lam B1) (fo.o-lam B2) :- 
    pi x y\ tm->to _ x y => tm->to L (B1 x) (B2 y).
  tm->to L (ho.app L1) T :- map (tm->to L) L1 [Hd|Tl], 
    fo.mk-app Hd Tl T.
  tm->to L (ho.uva VM TL) T :- mem L (mapping (fv VO) (hv VM _)), 
    map (tm->to L) TL T1, fo.mk-app (fo.o-uva VO) T1 T.
